Classless Java

### 2015-09-23 paper/sections/Formalization.tex
add spaces in Fig1 Grammar
added Context and Subtyping rules
auxiliary function mtype(m,T)
updated auxiliary mtype

\begin{figure}[h]
\begin{grammar}
\production{
\e
}{
  \x\mid\MCall\e\m\es\mid\MCall{\C}\m\es\mid\MCall{\C\QM{.super}}\m\es\mid\obj
  }{expressions}\\
\production{
\obj
}{
\QM{new}\C\oR\cR\oC\T_1\f_1\QM;\ldots\T_k\f_k\QM;
\mh_1\oC\QM{return}\e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\e_n\QM{;}\!\cC
\cC
  }{object creation}\\
\production{
\metaVar{I}
}{
 \ann\ \QM{interface} \C_0\QM{extends}\C_1\ldots\C_k \oC\method_1\ldots\method_n\cC
  }{interface declaration}\\
\production{
\method
}{
 \QM{static}\mh\oC\QM{return}\e\QM{;}\!\cC
\mid 
\QM{default}\mh\oC\QM{return}\e\QM{;}\cC
\mid
\mh\QM{;}
  }{method declaration}\\
\production{
\mh
}{
 \T_0 \m  \oR\T_1\x_1\ldots\T_n\x_n\cR
  }{method header}\\
\production{
\ann
}{
  \mixinAnn|\emptyset
  }{annotations}\\
\end{grammar}
\caption{Grammar of ClassLess Java}
\label{Grammar}
\end{figure}

@@

>>>>

\begin{figure}[h]
\begin{grammar}
\production{
\e
}{
  \x\mid\MCall\e\m\es\mid\MCall{\C}\m\es\mid\MCall{\C\QM{.super}}\m\es\mid\obj
  }{expressions}\\
\production{
\obj
}{
\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\ 
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
  }{object creation}\\
\production{
\metaVar{I}
}{
 \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_k \oC\method_1\ldots\method_n\cC
  }{interface declaration}\\
\production{
\method
}{
 \QM{static}\ \mh\ \oC\QM{return}\ \e\QM{;}\!\cC
\mid 
\QM{default}\ \mh\oC\QM{return}\ \e\QM{;}\cC
\mid
\mh\QM{;}
  }{method declaration}\\
\production{
\mh
}{
 \T_0\ \m\ \oR\T_1\ \x_1\ldots\T_n\ \x_n\cR
  }{method header}\\
\production{
\ann
}{
  \mixinAnn|\emptyset
  }{annotations}\\
\end{grammar}
\caption{Grammar of ClassLess Java}
\label{Grammar}
\end{figure}

@@

Context:

\[ \Gamma = \epsilon \mid (x, C) : \Gamma  \]

Subtyping:

\[ \inferrule{}{T <: T} \]

\[ \inferrule{S <: T \\ T <: U}{S <: U}\]

\[ \inferrule{\emph{ann} \spc \textbf{interface} \spc C_0 \spc \textbf{extends} \spc C_1,...,C_k \{...\}}
{C_0 <: C_1 \\ ... \\ C_0 <: C_k} \]

Interface Table (IT):

A mapping from types \texttt{T} to interface declarations \texttt{L}. From the
interface table, we can read off the subtype relation between interfaces. The
subtype relation is given by the \textbf{extends} clauses in \texttt{IT}.

Auxiliary Definitions:

- \textsf{mtype(m, C)} : the signature of method m in C.

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C \{ \overline{M} \} \\ 
  E \spc m(\overline{D} \spc \overline{x}) \{ \text{return } e; \} \in M}
{ \textsf{mtype(m,T)} = \overline{D} \to E } \]

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C \{ \overline{M} \} \\ 
  m \notin M}
{ \textsf{mtype(m,T)} = \emptyset } \]

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C \text{ extends } C_1,...,C_k \{ \overline{M} \} \\ 
  E \spc m(\overline{D} \spc \overline{x}) \{ \text{return } e; \} \in M}
{ \textsf{mtype(m,T)} = \overline{D} \to E } \]

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\ 
  m \notin M}
{ \textsf{mtype(m,T)} = \bigcup \textsf{mtype}(m,\overline{D}) } \]

\[ \textsf{mmodifier(m, C)} = ? \]

\[ \textsf{mtype(m, C)} = ? \]

\[ \textsf{checksuper(C.super.m(e), A, C)} = ? \]

\yanlin{todo: add auxiliary functions}
\yanlin{todo: add subtyping rules}

### 2015-09-23 paper/sections/Overview.tex
updated auxiliary mtype

\lstinputlisting[linerange=46-50]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT2D

\lstinputlisting[linerange=54-57]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT3D

\lstinputlisting[linerange=61-64]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=ANIMAL

\lstinputlisting[linerange=68-73]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=HORSE

\lstinputlisting[linerange=77-89]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=93-94]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=PEGASUS

>>>>

\lstinputlisting[linerange=46-52]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT2D

\lstinputlisting[linerange=56-60]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=POINT3D

\lstinputlisting[linerange=64-67]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=ANIMAL

\lstinputlisting[linerange=71-76]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=HORSE

\lstinputlisting[linerange=80-92]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=BIRD

\lstinputlisting[linerange=96-97]{../UseMixinLombok/src/test/TestAnimal.java}% APPLY:linerange=PEGASUS
